---
title: "FEC 2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(RPostgreSQL)
```

# Database connection

First, create a connection to the PostgreSQL server. Then set the `connection` object in `knit` so that all `sql` chunks will be able to use it. 

```{r}
db <- src_postgres(
  dbname = "pres_elect", 
  host = "localhost",
  user = "postgres", 
  password = "postgres"
)
knitr::opts_chunk$set(
  connection = db$con, 
  max.print = 25
)
```

# Option 1: Use `sql` chunks

Set the [`output.var` chunk option](https://bookdown.org/yihui/rmarkdown/language-engines.html#sql) to the name of the data frame you want that chunk to return. In this case, that data frame is called `warrens`. (See the Markdown source file.)

```{sql, output.var="warrens"}
SELECT * FROM candidate_master_info 
WHERE cand_name LIKE '%WARREN%'
LIMIT 1000;
```

Now, the data is available in our R session!

```{r}
as_tibble(warrens)
```

This method is nice and elegant, but harder to work with in your R session. 

# Option 2: Use `DBI`

```{r}
warrens_df <- DBI::dbGetQuery(db$con, "
  SELECT * FROM candidate_master_info 
WHERE cand_name LIKE '%WARREN%'
LIMIT 1000;
")
as_tibble(warrens_df)
```

This method works well, but you lose all syntax highlighting for the SQL queries so it looks ugly. 

# Running command line programs from within R

Use the `system2()` command to pass shell commands through and capture the output. 

```{r}
system2("ls", args = "-lhS", stdout = TRUE)
```